A better way to format your document for CEUR-WS

### 2024-06-24 paper/paper-part2.tex
Introductin added

From~\cite{jiao20}: Language model pre-training, such as BERT, has significantly improved the performances of many natural language processing tasks. However, pre-trained language models are usually computationally expensive, so it is difficult to efficiently execute them on resource-restricted devices. To accelerate inference and reduce model size while maintaining accuracy, we first propose a novel Transformer distillation method that is specially designed for knowledge distillation (KD) of the Transformer-based models. By leveraging this new KD method, the plenty of knowledge encoded in a large teacher BERT can be effectively transferred to a small student Tiny-BERT. Then, we introduce a new two-stage learning framework for TinyBERT, which performs Transformer distillation at both the pretraining and task-specific learning stages. This framework ensures that TinyBERT can capture he general-domain as well as the task-specific knowledge in BERT.
TinyBERT with 4 layers is empirically effective and achieves more than 96.8\% the performance of its teacher BERTBASE on GLUE benchmark, while being 7.5x smaller and 9.4x faster on inference. TinyBERT with 4 layers is also significantly better than 4-layer state-of-the-art baselines on BERT distillation, with only about 28\% parameters and about 31\% inference time of them. Moreover, TinyBERT with 6 layers performs on-par with its teacher BERTBASE.

>>>>

From~\cite{jiao20}: There are many advantages to TinyBERT compared to others, especially in efficiency and performance. Among them, one significant benefit is the reduced size with faster inference time: TinyBERT4, which contains only four layers, is 7.5 times smaller with 9.4 times faster than its teacher model, BERTBASE. Even with this massive drop in model size, TinyBERT4 can achieve more than 96.8\% of the performance compared to BERTBASE on all GLUE benchmark tasks, which proves that it can hold a high degree of accuracy while being substantially more efficient. In that case, TinyBERT will be particularly fitting for applications executed on devices under highly resource-restrictive conditions with limited computational power and memory.

Another major innovation of TinyBERT, however, is a new two-stage learning framework that includes general and task-specific distillation. The first is the general distillation stage, in which TinyBERT learns from the original BERT for general domain knowledge mastery.  After that, it will conduct task-specific distillation with the fine-tuned BERT for some downstream tasks so that task-specific knowledge can be absorbed into TinyBERT. In this two-phase process, the TinyBERT inherits all the rich, general knowledge from BERT and can further enhance its performance on specific tasks, making it more adaptable and effective in various natural language processing tasks.

More than that, TinyBERT's advanced distillation techniques include attention-based and hidden states-based ones. Specifically, these methods have been designed to distill the linguistic knowledge the teacher model has encoded in its attention weights and hidden states into the student model. When distilling, this technique enables TinyBERT to retain all essential features concerning syntax and coreference resolution tasks. The complementarity of these distillation techniques makes it possible for TinyBERT, with fewer parameters and reduced computational cost, to realize high performance. Finally, TinyBERT shows better performance compared with the other state-of-the-art models mainly designed for model compression. As shown, TinyBERT4 significantly outperforms other 4-layer models like BERT4-PKD and DistilBERT4 by at least 4.4\% while having only about 28\% of parameters and 31\% of inference time compared to these models. When scaled up to six layers, TinyBERT6 is on par with BERTBASE in performance; therefore, this makes it a relatively robust and scalable solution for a wide array of NLP tasks. Of course, all these advantages make TinyBERT one of the best choices for an application requiring efficient, high-performance language models.\\

### 2024-06-24 paper/paper.tex
Introductin added

CEUR-WS's article template provides a consistent \LaTeX{} style for
use across CEUR-WS publications, and incorporates accessibility and
metadata-extraction functionality. This document will explain the
major features of the document class.

If you are new to publishing with CEUR-WS, this document is a valuable
guide to the process of preparing your work for publication.

>>>>

Neural Information Retrieval has been a sea change for the field of Information Retrieval, driving unparalleled effectiveness improvements across a broad portfolio of IR tasks. However, these complex neural models bring traditional challenges in terms of much-needed computational resources, especially for efficient training and inference. This efficacy vs. computational cost dichotomy enforces the need for global evaluation of NIR methods by performance and resources. The third ReNeuIR Workshop, co-located with ACM SIGIR, will occur in Washington D.C., USA, in July 2024. It thus furthers a critical discourse on the efficiency of NIR models, including empirical justifications for increasing model complexity into daylight, urging resource-efficient model developments, and total evaluation frameworks accounting for quality, efficiency, and environmental impacts.

Our contribution to this discourse is also focused on optimizing TinyBERT, a lightweight language model. First, we will train various models with gradually tuned hyperparameters toward their minimization in size, subject to effectiveness. Such techniques shall be utilized at the interaction between hyperparameter optimization and model pruning for these goals.

To further boost the performance of our optimized TinyBERT models, we incorporate BM25 scores. Since BM25 has been one of the most successful traditional IR models based on probabilistic retrieval, we would like to combine the BM25 scores and the output from TinyBERT to create a synergistic effect for better retrieval performance without adding too much computational overhead.

Moreover, knowledge distillation will be utilized to gain efficiency and effectiveness. That is transferring knowledge from a large, well-performing teacher model to a smaller, more efficient student model. We can expect iterative distillation and finetuning to realize models that balance high effectiveness with low computational requirements.

This paper discusses an in-depth understanding of TinyBERT with hyperparameter optimization, BM25 integration, and knowledge distillation toward developing efficient NIR models. We work towards a long-term vision for sustainable and effective neural information retrieval—themes and motivations that best fit the ReNeuIR Workshop.
